Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-04-25 WSSSPE1_report/WSSSPE1_summary_report.tex
Abstract: refine.

\begin{abstract} %\note{Lead: Sou-Cheng T. Choi}
% Anne: Added a lead-in motivator to address the submission as a Experience paper
% and tried to improve writing... ( I am assumeing no abstract word count limit...)
Challenges related to the development, deployment, and maintenance of 
reusable software for science are becoming a growing concern. 
There are now many scientists whose research increasingly depends on 
the quality and availability of software they can use and build on. 
At the same time, software specialists have more than enough to do 
without having to ``reinvent the wheel.'' To highlight some of these 
issues and share experiences, The First Workshop on Sustainable 
Software for Science: Practice and Experiences (WSSSPE1) was held 
in November 2013 at SC13.
The workshop featured keynote presentations and based its discussion 
on them, as well as on a large number (54) of solicited extended abstracts 
that were grouped into three themes presented via panels that encouraged 
audience participation. A set of collaborative notes was taken during the workshop.

This document summarizes 
the issues and shared experiences discussed at the workshop, including
cross-cutting issues and use cases. It joins a nascent
literature seeking to understand what drives software work in science,
and how it is impacted by the reward systems of science. 
These incentives can determine the extent to which
developers are motivated to build software for the long-term, for the
use of others, and whether to work collaboratively or separately. We 
also elabroate on community building, leadership, and dynamics leading to 
successful scientific software.

>>>>

\begin{abstract} %\note{Lead: Sou-Cheng T. Choi}
% Anne: Added a lead-in motivator to address the submission as a Experience paper
% and tried to improve writing... ( I am assumeing no abstract word count limit...)
Challenges related to development, deployment, and maintenance of 
reusable software for science are becoming a growing concern. 
Research of many scientists now increasingly depends  on 
the quality and availability of software upon which their works are built. 
At the same time, software specialists have more than enough to do 
without having to ``reinvent the wheel.'' To highlight some of these 
issues and share experiences, the First Workshop on Sustainable 
Software for Science: Practice and Experiences (WSSSPE1) was held 
in November 2013 in conjunction with the Supercomputing Conference SC13.
The workshop featured keynote presentations and based its discussion 
on them, as well as on a large number (54) of solicited extended abstracts 
that were grouped into three themes presented via panels that encouraged 
audience participation. A set of collaborative notes was taken during the workshop.

This document summarizes 
the issues and shared experiences discussed at the workshop, including
cross-cutting issues and use cases. It joins a nascent
literature seeking to understand what drives software work in science,
and how it is impacted by the reward systems of science. 
These incentives can determine the extent to which
developers are motivated to build software for the long-term, for the
use of others, and whether to work collaboratively or separately. We 
also explore on community building, leadership, and dynamics in relation to
successful scientific software.
